Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-03-08 output/paper/_figures.qmd
Started reviewing manuscript based on co-authors comments.

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on the glucocorticosteroids expressed in ng/ml (HELIX subcohort; 2013-2016).** 
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5, is_cortisol = TRUE)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. Abbreviations: cortisone production (cortisone prod.); cortisol production (cortisol prod.); corticost. prod. (corticosterone production).
:::

>>>>

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020].
:::

@@

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the {{< acr edcs first_use=true >}} on the glucocorticosteroids expressed in ng/ml (HELIX subcohort; 2013-2016).** 
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020].
:::

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5, is_cortisol = TRUE)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020]. Abbreviations: cortisone production (cortisone prod.); cortisol production (cortisol prod.); corticost. prod. (corticosterone production).
:::

### 2024-03-08 output/paper/_si.qmd
Started reviewing manuscript based on co-authors comments.

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name) |>
  dplyr::group_by(class) |>
  dplyr::arrange(
    short_name,
    .by_group = TRUE
  )
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Information about non-persistent {{< acr edcs >}}, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.**
:::

@@

::: {#supptbl-codebook-1}
```{r codebook-1}
codebook_1
```
**Codebook for the covariates used in the estimation of the marginal comparisons of {{< acr edcs >}} on {{< acr hitrtse >}}.**
:::

::: {#supptbl-codebook-2}
```{r codebook-2}
codebook_2
```
**Codebook for the covariates used in the estimation of the marginal comparisons of {{< acr edcs >}} on the glucocorticosteroids.**
:::

::: {#supptbl-codebook-3}
```{r codebook-3}
codebook_3
```
**Codebook for the covariates used in the estimation of the marginal comparisons of the glucocorticosteroids on {{< acr hitrtse >}}.**
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  dplyr::left_join(edcs, by = c("exposure" = "chem_id")) |>
  dplyr::select(-exposure) |>
  dplyr::rename(Exposure = "short_name") |>
  dplyr::relocate(Exposure) |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: {{< acr edcs >}}; outcome: {{< acr hitrtse >}}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  dplyr::left_join(edcs, by = c("exposure" = "chem_id")) |>
  dplyr::select(-exposure) |>
  dplyr::rename(Exposure = "short_name") |>
  dplyr::relocate(Exposure) |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: {{< acr edcs >}}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::rename(Exposure = "exposure") |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: {{< acr hitrtse >}}) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights (exposures: {{< acr edcs >}}; outcome: {{< acr hitrtse >}}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights (exposures: {{< acr edcs >}}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: glucocorticosteroids; outcome: {{< acr hitrtse >}}) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: {{< acr edcs >}}; outcome: {{< acr hitrtse >}}; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: {{< acr edcs >}}; outcomes: glucocorticosteroids; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: glucocorticosteroids; outcome: {{< acr hitrtse >}}; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
**Measurement classification of {{< acr edcs >}}, by cohort (HELIX subcohort; 2013-2016).** 
Coding: 1, quantifiable; 2, <LOD; 3, interference or out of range; 4. not analysed.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on the glucocorticosteroids expressed in ng/ml (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} expressed in {{< acr mss >}}
 (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. Abbreviations: cortisone production (cortisone prod.); cortisol production (cortisol prod.); corticost. prod. (corticosterone production).
:::

>>>>

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name) |>
  dplyr::group_by(class) |>
  dplyr::arrange(
    short_name,
    .by_group = TRUE
  )
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Information about non-persistent {{< acr edcs first_use=true >}}, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.**
:::

@@

::: {#supptbl-codebook-1}
```{r codebook-1}
codebook_1
```
**Codebook for the covariates used in the estimation of the marginal comparisons of {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}}.**
:::

::: {#supptbl-codebook-2}
```{r codebook-2}
codebook_2
```
**Codebook for the covariates used in the estimation of the marginal comparisons of {{< acr edcs first_use=true >}} on the glucocorticosteroids.**
:::

::: {#supptbl-codebook-3}
```{r codebook-3}
codebook_3
```
**Codebook for the covariates used in the estimation of the marginal comparisons of the glucocorticosteroids on {{< acr hitrtse first_use=true >}}.**
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  dplyr::left_join(edcs, by = c("exposure" = "chem_id")) |>
  dplyr::select(-exposure) |>
  dplyr::rename(Exposure = "short_name") |>
  dplyr::relocate(Exposure) |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  dplyr::left_join(edcs, by = c("exposure" = "chem_id")) |>
  dplyr::select(-exposure) |>
  dplyr::rename(Exposure = "short_name") |>
  dplyr::relocate(Exposure) |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::rename(Exposure = "exposure") |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
**Summary statistics of the estimated balancing weights (exposures: glucocorticosteroids; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: glucocorticosteroids; outcome: {{< acr hitrtse first_use=true >}}; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
**Measurement classification of {{< acr edcs first_use=true >}}, by cohort (HELIX subcohort; 2013-2016).** 
Coding: 1, quantifiable; 2, <LOD; 3, interference or out of range; 4. not analysed.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020].
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the {{< acr edcs first_use=true >}} on the glucocorticosteroids expressed in ng/ml (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020].
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020]. Abbreviations: cortisone production (cortisone prod.); cortisol production (cortisol prod.); corticost. prod. (corticosterone production).
:::

### 2024-03-08 output/paper/_tables.qmd
Started reviewing manuscript based on co-authors comments.

dplyr::bind_cols(t1$`_data`, t2$`_data`) |>
  dplyr::select(-`class...4`, -`variable...5`) |>
  dplyr::rename(
    class = "class...1",
    variable = "variable...2"
  ) |>
  dplyr::left_join(
    edcs,
    by = c("variable" = "chem_id")
  ) |>
  dplyr::select(-variable) |>
  dplyr::rename(variable = "short_name") |>
  gt::gt(
    rowname_col = "variable",
    groupname_col = "class"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_footnote(
    footnote = "Estimate and 95% CI.",
    locations = gt::cells_column_labels()
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Pairwise differences between sex-specific marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of {{< acr edcs >}} on {{< acr hitrtse >}}, expressed in {{< acr mss >}}, and the glucocorticosteroids, expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).**
:::

>>>>

dplyr::bind_cols(t1$`_data`, t2$`_data`) |>
  dplyr::select(-`class...4`, -`variable...5`) |>
  dplyr::rename(
    class = "class...1",
    variable = "variable...2"
  ) |>
  dplyr::left_join(
    edcs,
    by = c("variable" = "chem_id")
  ) |>
  dplyr::select(-variable) |>
  dplyr::rename(variable = "short_name") |>
  gt::gt(
    rowname_col = "variable",
    groupname_col = "class"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_footnote(
    footnote = "Estimate and 95% CI.",
    locations = gt::cells_column_labels()
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Pairwise differences between marginal contrasts of males and females, for the effect of a decrease from the 90th to the 10th percentile of {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}}, expressed in {{< acr mss >}}, and on the glucocorticosteroids, expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between marginal contrasts of males and females, for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).**
:::
